An Introduction to Rocker: Docker Containers for R

### 2017-06-23 manuscript.Rmd
hard wrap for better diffs

Relative to `stable`, the `debian:testing` stack thus offers the following advantages:

@@

```
wget -qO- https://get.docker.com/ | sh
sudo docker run -d -p 80:8787 -e PASSWORD=<PICK-A-PASSWORD> rocker/rstudio
```

>>>>

Relative to `stable`, the `testing` stack thus offers the following advantages:

@@

    wget -qO- https://get.docker.com/ | sh 
    sudo docker run -d -p 80:8787 -e PASSWORD=<PICK-A-PASSWORD> rocker/rstudio
